---
title: "Homework 2"
output: html_notebook
---

| Homework 2                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Sep 6   | Business Analytics Graduate Program |
| Submit via GitHub              |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 2. Refer to the corresponding materials and
ICE (with solutions) posted on ICON.

To complete the homework, fill in the commands needed to finish all of
the exercises below. Program everything inside this notebook and do not
change the notebook's filename. If the exercises request that you store
information within certain variables, use those specific variables names
(case sensitive). This will assist in grading your homework in a timely
manner.

For notebooks in general:

- Comment your code so that a classmate, for example, could easily
follow along.

- Load any required packages using the `library(...)` command.
However, a notebook should *not* have any `install.packages(...)` or
`update.packages()` commands.

- Do not use the `View(...)` command in a notebook. Viewing a data
frame should be done interactively using RStudio's console but is not
recommended for a notebook that will be run by someone else.

For homeworks in general:

- Be careful not to alter any supplied data files. In particular, if you
open a CSV file with Excel, do *not* save it with Excel.

- Before turning in a homework, run your entire notebook by choosing
*Run > Restart R and Run All Chunks* in the RStudio interface.
Everything should work without error!

- To turn in a homework, unless otherwise instructed, upload *only* your
notebook to your corresponding GitHub repository. Please do not change
the notebook's filename. GitHub overwrites the previous version of the
file when you upload your version.

- If given a data set, there is no need to upload that data set back
into GitHub. Also, if your code generates any ouput files, such as an
HTML file, a new data set, or an image, then there is no need to upload
those files either.

Also included with this homework are the solutions within the included
file `soln.Rdata`. If you would like to see the solutions, execute
this command in the console: `load("soln.Rdata", soln <- new.env())`.
Then you can access the solutions within the object called `soln`. For
example, `View(soln$df)` will show the contents of the correct data
frame `df`. These are for your reference. The purpose of the homework is
for you to create these solutions on your own. Points will be deducted
if your turned-in notebook uses `soln.Rdata` in any way.

# Exercises

For exercises #1-8, carefully review the included files `fires.txt`
(!), `fires.png`, and `fires.csv`. Exercises #9-11 use `mcd.csv`, which
contains nutritional information for items on McDonald's menu.

```{r}

```

## #1

Read `fires.csv` into a data frame df according to the following table:

    Input Column Name      Class                New Column Name
    -----------------      -----                ---------------
    alm_date               Date                 date
    station                factor               (no change)
    zip                    integer              zipcode
    combined adress        character            address
    latitude               numeric              (no change)
    longitude              numeric              (no change)
    inci_type              factor               incident_type_code
    descript               character            incident_type
    prop_use               factor               property_use_code
    descript_b             character            property_use

For all other columns that exist in the CSV file, either do not read
them in or, if you do read them in, eliminate them afterwards. Note
that, in R, `double` is synonymous with `numeric` but that `integer` is
different than `numeric`.

```{r}

```

## #2

Remove all rows that have one or more pieces of missing of data.

```{r}

```

## #3

Alter the levels of `df$station` according to the following: "1"
changes to "Downtown", "2" to "West", "3" to "Southeast", and "4" to
"Northeast". [Hint: Please follow capitalization as shown.]

```{r}

```

## #4

Use `format(..., "%b")` as part of a single command to create a new
column `df$month`, which contains the month in which the fire occurred.
For example, the date `2012-03-13` would show as `Mar` in the new
column. Also make `df$month` a factor.

```{r}

```

## #5

Create a new variable `df$east`, which is a factor with levels "1" if
the station corresponds either to "Northeast" or "Southeast" and "0"
otherwise.

```{r}

```

## #6

Remove all rows in which the zip code is *not* one of 52240, 52242,
52245, or 52246. [Note: Why remove certain zip codes? These are the ones
in which very few fires occurred.]

```{r}

```

## #7

Filter the data frame to keep only records with latitude measurements
between 41.6 and 42.0 (inclusive) and longitude measurements between
-91.75 and -91.45 (inclusive).

```{r}

```

## #8

Make sure the levels of the month column are sorted in the usual
calendar order, i.e., "Jan", "Feb", ..., "Dec". Then write df to
a csv file called "fires_df.csv".

```{r}

```

## #9

Use `read_csv(...)` to read `mcd.csv` into a data frame called `food`.
You can use all of defaults of `read_csv`.

```{r}

```

## #10

Assuming the daily requirement for calories is 2,000, create a new
column called `CaloriesPerc` that gives the percentage of daily
calories---on a scale of 0 to 100---contributed by a single serving of
each item. Afterwards, delete the `Calories` column. [Hint: Do not round
the result in `CaloriesPerc`.]

```{r}

```

## #11

Simultaneously reorder the contents of food in decreasing order of
`CaloriesPerc` and then increasing order of `Protein`. Then write food
data frame to a csv file called "food_df.csv".

```{r}

```
